---
title: "Triple-barrier-labelling"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{triple_barrier_labeling}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



In these vignette we will show how to use triple barrier labelling in 2 cases:

1. Without primary model.
2. With primary model (meta labelling).

First lets import packages and sample data from `mlfinance` package:

```{r message=FALSE,warning=FALSE}
# import packages
library(data.table)
library(mlfinance)

# import sample data
data(spy)

```

Data contains SPY market data with 5 minute frequency for period from 2018-01-01 to 2020-01-01.

Next, we will calculate daily volatility. There are many options of how to calculate daily volatility from intraday data.
Probably best approach would be to calculate realized volatility, but for our simple case we will `daily_volatility` function from the package.

```{r}
# compute daily volatility
daily_vol <- daily_volatility(spy[, c('index', 'close')], 50)

```

